% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{multicol}
%\usepackage[top=.5in, bottom=.5in, left=.5in, right=.5in]{geometry}


\begin{document}
\setlength\columnsep{-30pt}
%\setlength{\multicolsep}{6.0pt plus 2.0pt minus 1.5pt}% 50% of original values
\name{Connor F. Henley}
\email{cxh1451@rit.edu}
\phone{me@connorhenley.engineer}
\address{blank}
\address{blank}
\website{https://connorhenley.engineer}
\website{}
 
\begin{resume}
 \setlength
 \multicolsep{2pt}

\section{OBJECTIVE} % CAREER OBJECTIVE for real resume
	To get a job as a Residence Advisor, which will allow me to assist residents with their transition to college life and help residents succeed during their time at RIT.
 
\section{LEADERSHIP EXPERIENCE} % change to experience for non-ra resume
	%{\sl Test Engineer Co-op} \hfill {\sl January 2016 - May 2016}\\
	%	Space Exploration Technologies, Hawthorne CA
	%	\begin{itemize}  \itemsep -2pt % reduce space between items
	%		\item Created software to automate the creation of trouble reports
	%		\item Developed tests to test flight avionics hardware
	%		\item Troubleshot issues with avionics test racks
	%	\end{itemize}
	%\vspace{-5pt}

	{\sl FIRST Robotics} \hfill {\sl October 2009 - Current}\\
		Multiple Teams, in Colchester CT or Rochester NY
		\begin{itemize}
			\itemsep -2pt
			\item \textit{October 2009 - December 2011} 
			\item Was a student on the local FIRST Lego League teams 
			\item Led the team in 2011, and we won an award and went to States
			\item \textit{September 2012 - April 2016}
			\item Was a student on FIRST Robotics Competition Team 1699
			\item Started as a programmer and electrician on the controls team
			\item Worked on pit crew (got the robot ready for the next match) in 2013
			\item Got chosen to be a member of Drive Team in 2014
			\item Started voulenteering at events in April 2014
			\item Ran successfully for controls lead in early 2015
			\item Led the design team for the grabber in 2015
			\item Ran successfully for co-captain of the team in late 2015
			\item Under my lead, the controls team won the Innovation in Controls Award in 2016
			\item \textit{April 2016 - Current}
			\item Mentored multiple FIRST teams, taught programming to elementary and high school students
		\end{itemize}

\section{PROJECTS}
	%{\sl High Altitude Balloon Telemetry Tracker }
	%	\begin{itemize} 
	%		\itemsep -2pt
	%		\item Personally developed hardware and software design and implementation
	%		\item Developing radio board to have the ability to use FSK, AFSK, or audio-based protocols
	%		\item Utilized multiple PCBs in order to separate functionality and increase reusability
	%		\item Can communicate GPS and other sensor data to the Amateur Radio APRS network
	%		%\item Required PCB design and construction, embedded programming, protocol implementation, RF implementation knowledge
	%	\end{itemize}
	
	{\sl Swerve Code for Team 1699}
		\begin{itemize} 
			\itemsep -2pt
			\item Wrote code for a swerve drivetrain, which is a drivetrain where all wheels are independently steered and driven
			\item Incoroprated PID loops in order to make the steering motions smoother and to automatically adjust for drift.
			\item Though we never got the physical modules to test the code, the code can be found on GitHub.
		\end{itemize}

	\vspace{-8pt}
	{\sl ini-reader and ini-editor for Team 1699}
		\begin{itemize}
			\itemsep -2pt
			\item Rewrote code to read configuration files stored on the robot. The original project was written in LabView, but we moved to Java.
			\item Besides rewriting the project, I added to it, adding lots of aditional functions to the original project.
			\item Currently, the code has been used on the 2016 and 2017 robot and in the swerve code.
			\item The ini-editor was written to make the editing of configuration files on the robot easier, and the simulator was written to show how a configuration file is read into memory.
			\item The user interface was written in Python with TK and the simulator was written in Java with JavaFX, and all code can be found on the Team 1699 GitHub.
		\end{itemize}

\section{AWARDS \& SKILLS} 
	%\\[-5ex]
		\begin{multicols}{2}
			\begin{itemize}
				\itemsep -2pt
				%\item[] example entry
				\item[] A+ Certified
				\item[] Network Pro Certified
				\item[] Chairman's Award from FIRST Team 1699
				\item[] filler

			\end{itemize}
		\end{multicols}	
	\vspace{-8pt}
	{Languages \& Software:} %\\%[-5ex]
		\begin{multicols}{2}
			\begin{itemize}
				\itemsep -2pt
				%\item[] example entry
				\item[] C and C++
				\item[] Turbo Pascal
				\item[] Python
				\item[] Java
				\item[] nginx and WordPress
				\item[] \LaTeX
				\item[] Microsoft Office
				\item[] Windows and Linux
			\end{itemize}
		\end{multicols}

\section{EDUCATION} 
	{\sl Bachelor of Science,} Computer Engineering, GPA: 3.28\\
        % \sl will be bold italic in New Century Schoolbook (or
	    % any postscript font) and just slanted in
		% Computer Modern (default) font
                Rochester Institute of Technology, Rochester NY, 
				Expected June 2021 %\\%[-5ex]
				\begin{multicols}{2}
					\begin{itemize}
						\itemsep -2pt
						%\item[] example entry
						\item[] Computer Science I and II
						\item[] Calculus I and II
						\item[] Intro to Psychology
						\item[] Intro to Philosophy
						\item[] Intro to International Relations
						\item[] Intro to Computer Engineering						
					\end{itemize}
					Currently taking:
					\begin{itemize}
						\itemsep -2pt
						\item[] Mechanics of Programming
						\item[] Multivariable Calculus
						\item[] Digital Systems Design I
						\item[] Physics I
						\item[] Writing Seminar
					\end{itemize}
				\end{multicols}
 	
	{\sl High School Diploma,} GPA: 3.6(add to me)\\
				Bacon Academy, Colchester CT,
				Recived June 2016
				\begin{multicols}{2}
					\begin{itemize}
						\itemsep -2pt
						%\item[] example entry
						\item[] AP Human Geography
						\item[] AP Computer Science AB
						\item[] AP Calculus AB
						\item[] AP Physics 1
					\end{itemize}
				\end{multicols}
\vspace{8pt}
\section{COMMUNITY \\ SERVICE}  
	%{\sl	Assistant Scoutmaster at Boy Scout Troop 88, North Adams, MA}
	%\begin{itemize}  \itemsep -2pt %reduce space between items
	%	\item Mentored Scouts to achieve rank and acquire valuable life skills% and become better Scouts 
	%	\item Assisted with multiple community service projects
	%\end{itemize}
	%\vspace{-5pt}

	{\sl Mentoring FIRST Robotics Teams}
	\begin{itemize}  
		\itemsep -2pt
		\item Mentored FIRST Team 1699 in Colchester CT, teaching programming and electronics
		\item Mentored FIRST Lego League <fill> in Rochester NY, teaching programming and team values
	\end{itemize}

	{\sl Voulenteering at FIRST Events}
	\begin{itemize}
		\itemsep -2pt
		\item Started Voulenteering in 2014 at the Hartford District Event doing field reset.
		\item Voulenteered at the 2015 Waterbury District Event doing scoring.
		\item Voulenteered at the 2016 Connecticut State Championship doing field reset.
		\item Signed up to voulenteer at the 2017 Finger Lakes Regional doing field reset.
	\end{itemize}

\section{PERSONAL INTERESTS \\ AND HOBBIES}             
	Member of RIT FIRST Robotics Club\\

\end{resume}

\end{document}