% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{multicol}
%\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}


\begin{document}
\setlength\columnsep{-30pt}
%\setlength{\multicolsep}{6.0pt plus 2.0pt minus 1.5pt}% 50% of original values
\name{Christopher R. Culpepper}
% \address used twice to have two lines of address
\address{56 South Street Drury, MA}
\address{CRC3510@RIT.EDU}
\address{(413) 376-5034}

 
\begin{resume}
 \setlength\multicolsep{2pt}

\section{OBJECTIVE}   
	A Co-Op position in the field of Computer Engineering for the Spring and Summer of 2016 for the purpose of furthering my education.  
 
\section{EDUCATION} {\sl Bachelor of Science,} Computer Engineering \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Rochester Institute of Technology, Rochester NY, 
				Expected May 2017 %\\%[-5ex]
				\begin{multicols}{2}
					\begin{itemize}
							\itemsep -2pt
						\item[] Assembly Language Programming
						\item[] Applied Programming
						\item[] Digital System Design
						\item[] Computer Organization
						\item[] Introduction to Software Engineering
						\item[] Computer Science
						\item[] Calculus I-III
						\item[] Physics I-II
					\end{itemize}
				\end{multicols}
 
\section{COMPETENCES AND SKILLS} 
	%\\[-5ex]
		\begin{multicols}{2}
			\begin{itemize}
				\itemsep -2pt
				\item[] Eagle Scout
				\item[] A+ Certified
				\item[] Microsoft Office
				\item[] OSHA10 Certified
				\item[] Maintaining Linux and Windows Systems
			\end{itemize}
		\end{multicols}
	{Languages \& Software:} %\\%[-5ex]
		\begin{multicols}{2}
			\begin{itemize}
				\itemsep -2pt
				\item[] C/C++
				\item[] Python
				\item[] VHDL
				\item[] Visual Basic for Applications (VBA)
				%\item[] Java
				\item[] ARM \& HCS12 Assembly
				\item[] AutoIt
				\item[] \LaTeX 
			\end{itemize}
		\end{multicols}
\section{EXPERIENCE} 
{\sl Systems Engineering Co-Op} \hfill {\sl July 2013 - January 2015 }\\
	General Dynamics Advanced Information Systems, Pittsfield MA
	\begin{itemize}  \itemsep -2pt % reduce space between items
			\item Performed both software and systems testing on 
				control software. 
			\item Helped to develop an automatic tracker for
				testing that was used to status testing progress
				to management. 
			\item Developed an application to measure and track 
				code base sizes to assist with the peer review process.
	\end{itemize}
 
	{\sl Information Technology Intern} \hfill {\sl May 2011 - January 2013} \\
		MountainOne Financial Partners, North Adams, MA
		\begin{itemize}  \itemsep -2pt %reduce space between items
			\item Manned internal help desk for low to mid-size bank.
			\item Developed custom storage solution for internal data.
			\item Repaired and maintained servers, laptops and desktops. 
		\end{itemize} 

		{\sl Assembly Language Lab Teaching Assistant } \hfill {\sl January 2015 - Present} \\
		Computer Engineering Department, RIT, Rochester, NY
		\begin{itemize}  \itemsep -2pt %reduce space between items
			\item Responsible for grading student reports and assisting students with ARM assembly language. 
		\end{itemize} 
 
\section{COMMUNITY \\ SERVICE}  
	Adult leader in Boy Scout Troop 88, North Adams, MA
	\begin{itemize}  \itemsep -2pt %reduce space between items
		\item Assistant Scoutmaster
		\item Mentored Scouts to achieve rank and acquire valuable life skills% and become better Scouts 
	\end{itemize}
	Radio communication at multiple road rallies:
	\begin{itemize}  \itemsep -2pt %reduce space between items
		\item Responsible for maintaining communication for racing stage
		\item Relayed pertinent information to competitors, stage captain and race officials
	\end{itemize}

\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
	Amateur Radio Extra\\
	Member of the K2GXT RIT Amateur Radio Club\\
	Motorcycle repair\\
	Camping and hiking\\
	Currently developing a communications controller for telemetry and imaging for a high altitude balloon. \\


\end{resume}
\end{document}







